Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-29 Ch1_movement_rates/Ch1_Figures.Rmd
I think results might be ready

evd.fit.cp <-fevd(cp.evd$disp, threshold = tval.cp, type = "GP")
evd.fit.pp <- fevd(pp.evd$disp, threshold = tval.cp, type = "GP")
evd.fit.np <- fevd(np.evd$disp, threshold = tval.cp, type = "GP")

summary(evd.fit.cp)
summary(evd.fit.pp)
summary(evd.fit.np)

@@

# To find the probability of exceeding 1000, 5000, or 10,000 meters based on the fitted ged 
dist_range <- c(200, 500, 1000, 5000, 10000)

pextRemes(evd.fit.cp, dist_range, lower.tail = FALSE)
pextRemes(evd.fit.pp, dist_range, lower.tail = FALSE)
pextRemes(evd.fit.np, dist_range, lower.tail = FALSE)

# Not sure this is right though. I want the conditional probability that a dispersal distance that is already over the threshold goes beyong 1000, 5000, and 10000 meters.

@@

>>>>

evd.fit.cp <- fevd(cp.evd$disp, threshold = tval.cp, type = "GP")
evd.fit.pp <- fevd(pp.evd$disp, threshold = tval.pp, type = "GP")
evd.fit.np <- fevd(np.evd$disp, threshold = tval.np, type = "GP")

cbind(c("CP", "PP", "NP"), rbind(evd.fit.cp$results$par,
      evd.fit.pp$results$par,
      evd.fit.np$results$par))

@@

# To find the probability of exceeding 1000, 5000, or 10,000 meters based on the fitted ged 
dist_range <- c(200, 500, 1000, 5000)

cbind(c("Distance", "CP", "PP", "NP"), rbind(dist_range,
                                             pextRemes(evd.fit.cp, dist_range, lower.tail = FALSE),
                                             pextRemes(evd.fit.pp, dist_range, lower.tail = FALSE),
                                             pextRemes(evd.fit.np, dist_range, lower.tail = FALSE)))

@@

Summary for the fits

```{r}
summary(evd.fit.cp)
plot(evd.fit.cp)
summary(evd.fit.pp)
plot(evd.fit.pp)
summary(evd.fit.np)
plot(evd.fit.np)
